A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 6_validation.tex
redo accuracy section

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the amount of the overfill and underfill. 
This is compared on a slice of a \jun{?} model, as shown in \cref{visualized_accuracy} (top).
\jun{discuss this figure a bit}

We further quantitatively compare the accuracy of the beading schemes on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

>>>>

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
\begin{wrapfigure}{r}{.3\columnwidth}
\centering
\includegraphics[width=.25\columnwidth]{sources/validation/visualization_principle_rounded_excluded_single.pdf}
\caption{
Extrusion segments coverage.
The hole at the end will be filled by the next extrusion segment.
}
\label{segment_visualization_simple}
\end{wrapfigure}
We construct the over- and underfill area by comparing the shapes covered by each extrusion move (\cref{segment_visualization_simple}) with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.

We compare the total area (in \si{\milli\meter\squared}) of these overfill and underfill shapes to the total area of the boundary for each sample in the data set.
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.
